Vectorizing Python Constructs Using Pythran and Boost SIMD

### 2013-11-25 doc/papers/wpmvp14/paper.tex
++Introduction

%%
%%
\section{Changing Python Semantic for Vectorization}

@@

%%
%%
\section{Vectorization of a Meta-Program}

@@

%%
%%
\section{Validation of the Approach using the Pythran Compiler}

>>>>

Pythran is also an AOT compiler, which holds the uinique property of turning
Python modules into C++ \emph{meta-programs}. It does not need type annotations
and keeps the polymorphism of original functions, respecting Python's duck
typing. Like other AOT compilers, it unboxes all variables for better
performance, and performs a wide variety of optimizations such as lazy
evaluation, constant folding, expression fusion etc.  It supports core
\texttt{numpy} constructs and most Python constructs to the notable exception
of user classes. Constructs such as \texttt{eval}, are not supported.

This paper introduces vectorization of Python programs based on the idea that
many Python constructs already exhibit good vectorization opportunities. The
goal of the paper switches from automatic vectorization to vectorization of
high-level Python intrisics, as described in Section~\ref{sec:python-semantic}.
One of the difficulties of vectorizing Python functions is linked to function
polymorphism. Vectorization in the context of C++ meta-programs is examined in
Section~\ref{sec:meta-vectorization}. The approach is validated using the
Pythran compiler on several micro-applications from signal processing, physics
and mathematics presented in Section~\ref{sec:benchs}.

%%
%%
\section{Using Python Semantic for Vectorization}
\label{sec:python-semantic}

@@

%%
%%
\section{Vectorization of a Meta-Program}
\label{sec:meta-vectorization}

@@

%%
%%
\section{Validation of the Approach using the Pythran Compiler}
\label{sec:benchs}
